A Study of Target Following with X-Ray Vision in Augmented Reality

### 2009-06-25 Paper/paper.tex

\title{A Study of an X-Ray Vision Tracking Task in Simulated Augmented Reality}

@@

\author{
Submission 191
%Roy G. Biv\thanks{e-mail: roy.g.biv@aol.com}\\ Starbucks Research %
%\and Ed Grimley\thanks{e-mail:ed.grimley@aol.com}\\Nigel Mansell\thanks{nigelf1@msn.com}\\ Grimley Widgets, Inc. %
%\and Martha Stewart\thanks{e-mail:martha.stewart@marthastewart.com}\\ Martha Stewart Enterprises \\ Microsoft Research
}

@@

Augmented Reality systems may be used to simulate x-ray vision \cite{1383060}.  The ability to see through solid objects has potential applications in various fields ranging from construction \cite{Webster96augmentedreality}, medicine \cite{azuma95survey}, military \cite{Livingston02anaugmented} and search-and-rescue operations \cite{1528424}.  Unfortunately, implementing x-ray vision is not a trivial task.  AR systems have cost issules, including those pertaining to level-of-immersion.  For example, what is the ideal augmented field of view (FOV) for a given scenario?  Other issues relate to tracking the objects in the x-ray view, such as GPS dropout errors \cite{4079263}, where position information is temporarily lost.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=3in]{figures/tophatscreenshot.png}
	\caption{Sample user-view of AR simulation.  Top Hat is visible (non-occluded) in the doorway.  The augmented view overlays transparent red rectangles on the characters, indicating their location while occluded.}
\end{figure}

>>>>

\title{A Study of Target Following with X-Ray Vision in 
%Simulated
Augmented Reality}

@@

\author{
Submission 165
%Roy G. Biv\thanks{e-mail: roy.g.biv@aol.com}\\ Starbucks Research %
%\and Ed Grimley\thanks{e-mail:ed.grimley@aol.com}\\Nigel Mansell\thanks{nigelf1@msn.com}\\ Grimley Widgets, Inc. %
%\and Martha Stewart\thanks{e-mail:martha.stewart@marthastewart.com}\\ Martha Stewart Enterprises \\ Microsoft Research
}

@@

Augmented Reality systems may be used to simulate x-ray vision.  The ability to see through solid objects has potential applications in various fields ranging from construction \cite{Webster96augmentedreality}, medicine \cite{azuma95survey}, military \cite{Livingston02anaugmented} and search-and-rescue operations \cite{1528424}.  Unfortunately, implementing x-ray vision is not a trivial task.  AR systems have cost issules, including those pertaining to level-of-immersion.  For example, what is the ideal augmented field of view (FOV) for a given scenario?  Other issues relate to tracking the objects in the x-ray view, such as GPS dropout errors \cite{4079263}, where position information is temporarily lost.

A task common to many AR x-ray systems is to follow, using the augmented overlay, a moving target that is occluded by objects in the real world.  Problems with the AR system tracking objects accurately is often an issue which is likely to have an effect on task performance.  Since the augmented view is overlaid on top of the real view it is also interesting to study the effects of the augmented field of view s well as its interaction with tracking difficulties.  We created a task that aimed to accomplish these goals in a generic fashion in order to be generalizable while still being grounded in reality.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=3in]{figures/view_comp.png}
	\caption{Sample user-view of AR simulation.  Top Hat is visible (non-occluded) in the doorway.  The augmented view overlays transparent red rectangles on the characters, indicating their location while occluded.}
\end{figure}
